Pillar 1 - Sequential Pattern Mining

### 2019-02-05 Pillar 1 - Sequential Pattern Mining.Rmd
corrected confidence and lift

```{r TODO}
# TODO: corrected confidence for AR
```

@@

### Computing Support
```{r}

@@

    # include rhs.support
    mutate(
      rhs_course = str_remove_all(rhs, pattern = "_fail|_low|_not taken")
      ) %>%
    left_join(
      select(data_support, item, !!type_rule_enquo),
      by = c("rhs_course" = "item")
      ) %>%
    mutate(
      rhs.support = !!type_rule_enquo
      )

@@

#
# AR taken
AR_taken <- transactions %>%
  make_AR(
    data_support = d_support_take, 
    type_rule = rate.take
    )

@@

  # lhs and rhs must be fail
  filter(
    str_detect(lhs, "fail"),
    str_detect(rhs, "fail")
    )

@@

    # lhs and rhs must be low
  filter(
    str_detect(lhs, "low"),
    str_detect(rhs, "low")
    )

@@

AR_TPF <- transactions_TPF %>%
  make_AR(
    data_support = d_support_take, 
    type_rule = rate.take
  ) %>%

  # lhs and rhs must be low
  filter(
    str_detect(rhs, "fail")
    )

@@

# Make RA
AR_G <- transactions_G %>%
  my_apriori(appearance = NULL) %>%
  clean_AR %>%

>>>>

```{r TODO}

@@

### Support
```{r}

@@

    # rhs.support
    mutate(
      rhs_course = str_remove_all(rhs, pattern = "_fail|_pass|_low|_not taken")
      ) %>%
    left_join(
      select(data_support, item, !!type_rule_enquo),
      by = c("rhs_course" = "item")
      ) %>%
    mutate(
      rhs.support = !!type_rule_enquo
      )

@@

#
# AR taken (confidence and lift already correct)
AR_taken <- transactions %>%
  make_AR(
    data_support = d_support_take, 
    type_rule = rate.take
    )

@@

  # Confidence and Lift
  separate(
    rhs,
    sep = "_",
    into = c("rhs_course", "rhs_outcome"),
    remove = FALSE
    ) %>%
  group_by(
    lhs, rhs_course
    ) %>%
  mutate(
    lhs.rhsTake.support = sum(support),
    confidence          = support / lhs.rhsTake.support,
    lift                = confidence / rhs.support
    ) %>%
  ungroup %>%

  # lhs and rhs must be fail, count >= 5
  filter(
    str_detect(lhs, "fail"),
    str_detect(rhs, "fail"),
    count >= 5
    ) %>%
  select(
    - c(rhs_outcome, rhs_course)
  )

@@

  # Confidence and Lift
  separate(
    rhs,
    sep = "_",
    into = c("rhs_course", "rhs_outcome"),
    remove = FALSE
    ) %>%
  group_by(
    lhs, rhs_course
    ) %>%
  mutate(
    lhs.rhsTake.support = sum(support),
    confidence          = support / lhs.rhsTake.support,
    lift                = confidence / rhs.support
    ) %>%
  ungroup %>%

  # lhs and rhs must be fail, count >= 5
  filter(
    str_detect(lhs, "low"),
    str_detect(rhs, "low"),
    count >= 5
    ) %>%
  select(
    - c(rhs_outcome, rhs_course)
  )

@@

AR_TPF <- transactions_TPF %>%
  make_AR(
    data_support = d_support, 
    type_rule = rate.fail
  ) %>%

  # Confidence and Lift
  separate(
    rhs,
    sep = "_",
    into = c("rhs_course", "rhs_outcome"),
    remove = FALSE
    ) %>%
  mutate(
    rhs.take = str_detect(rhs, "fail|pass")
    ) %>%
  group_by(
    lhs, rhs_course
    ) %>%
  mutate(
    lhs.rhsTake.support = sum(support * rhs.take),
    confidence          = support / lhs.rhsTake.support,
    lift                = confidence / (rhs.support + 1e-4) # some courses have a failure rate of 0%.
    ) %>%
  ungroup %>%

  # lhs and rhs must be fail, count >= 5
  filter(
    str_detect(lhs, "not taken"),
    str_detect(rhs, "fail"),
    count >= 5
    ) %>%
  select(
    - c(rhs_outcome, rhs_course, rhs.take)
  )

@@

# Make AR
AR_G <- transactions_G %>%
  my_apriori(appearance = NULL) %>%
  clean_AR %>%
